%-------------------------
% Resume in Latex
% Author : Ahmed Ramdhan Ahmed Sidi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeLanguage}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ahmed Ramdhan Ahmed Sidi} \\ \vspace{1pt}
    Nouakchott, Mauritania \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +222 42170007 ~ \href{mailto:ahmedramdhan02@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{ahmedramdhan02@gmail.com}} ~ 
    \href{https://linkedin.com/in/ahmedramdhanas}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ahmedramdhanas}}  ~
    \href{https://github.com/rmdnhub}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/rmdnhub}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Diploma in Software Enginnering}{2022 -- 2024}
      {Ecole Supérieure Polytechnique de Nouakchott}{}
    \resumeSubheading
      {National Engineering Competition of Mauritania}{2020 -- 2022}
      {Preparatory Institute for Engineering Schools}{}
    \resumeSubheading
      {Mathematics Baccalaureate}{2017 -- 2020}
      {Lycée d'Excellence 1}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Banque Populaire de Mauritania}{November 2023 -- June 2024}
      {Fullstack Engineer Intern $|$ AWS, Docker, React.js, Django}{Apprenticeship}
      \resumeItemListStart
        \resumeItem{Developed an online learning platform for the bank's employees.}
        \resumeItem{Based on the Docker Devstack distribution of Open edX and using Jira Software for task management.}
        \resumeItem{Deployed the platform images on AWS using EC2, ECR, and ECS.}
      \resumeItemListEnd

    \resumeSubheading
      {Adias}{July -- August 2023}
      {Frontend Engineer Intern $|$ Angular, JavaScript, HTML, CSS}{Internship}
      \resumeItemListStart
        \resumeItem{Developed the front-end of a web-based learning application inspired by Udemy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Academic Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Mail Management System} $|$ \emph{Angular, Spring Boot, PostgreSQL, GitHub}}{January -- June 2024}
          \resumeItemListStart
            \resumeItem{Developed a fullstack application to manage the transmission, reading, response, and archiving of incoming and outgoing mail within a department.}
            \resumeItem{Used Angular for the frontend, Spring Boot for the backend, and PostgreSQL as the database.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{HafedhGPT} $|$ \emph{Machine Learning, API}}{November -- December 2023}
          \resumeItemListStart
            \resumeItem{Created and trained a custom ChatGPT model to predict exam patterns and provide tailored responses to my professor's course materials.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{School Management System} $|$ \emph{Python, Django, Flask, GitLab, Bootstrap}}{March -- June 2023}
          \resumeItemListStart
            \resumeItem{Led a three-person Agile team to develop a school management application.}
            \resumeItem{Developed one version of the application using Django and another version using Flask.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, VBA, C, C++, Java, JavaScript, TypeScript, Assembly, Prolog, PL/SQL} \\
     \textbf{Technologies}{: Angular, React.js, Flutter, Spring Boot, Django, Flask, Bootstrap, AWS, Docker, Git, Oracle, MySQL, PostgreSQL, MongoDB, Spark, Kafka, TensorFlow, Keras, Linux} \\
     \textbf{Development Tools}{: Visual Studio, Android Studio, IntelliJ, Eclipse, Jira Software, GitHub, GitLab, Postman} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------LANGUAGES-----------
\section{Languages}
  \begin{itemize}[left=0in, label={}, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \resumeLanguage{Arabic}{Native}
    \resumeLanguage{French}{DALF C2}
    \resumeLanguage{English}{TOEIC Listening B2 \& Reading B2}
  \end{itemize}

%-----------LEADERSHIP / EXTRACURRICULAR-----------
\section{Activities}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Huawei, Seeds for the Future} $|$ \emph{Entrepreneurship, Artificial Intelligence, Teamwork}}{September 2023}
          \resumeItemListStart
            \resumeItem{Participated in the "Seeds for the Future" program in Casablanca, Morocco, organized by Huawei to enhance young talents' skills in new technologies. With a team of Moroccan talents, we presented our idea for an application using artificial intelligence to reduce children's screen addiction. My team, GenZai, won first place in North Africa.}
          \resumeItemListEnd
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Mathematics Olympiad at the Baccalaureate Level}}{August 2020}
          \resumeItemListStart
            \resumeItem{Achieved fourth place, demonstrating expertise in problem-solving.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
